---
title: "744 Homework 2"
author: "Siyi Wang"
date: "2021/9/22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Statement of Jia You's online graphic

This graph is trying to show how effective the vaccine works for infectious diseases. 

**BMB: "how effectively the vaccine works against" or "how effective the vaccine is against"**

The example disease is Measles, and circles in this graph represent the number of reported cases of this disease.

It is easy to notice that, after $1963$, the Measles vaccine introduced, the number of reported cases showed a general decreasing trend and reached a very low level after $1980$, which proves the importance of the vaccine.

**BMB: don't need to typeset numbers in LaTeX (`$$`); this sets them in a font that's different from the rest of the text**

```{r}
library(ggplot2)
library(tidyverse)
data_dis<-read.csv("https://mac-theobio.github.io/DataViz/data/vaccine_data_online.csv")
```


# First GG plot
```{r}

## BMB: spaces around "<-" please
data <- data_dis %>% mutate(disease= factor(disease),
                            disease= reorder(disease,cases, Fun=mean))
## BMB: should be FUN not Fun (case-sensitive!). Harmless in this case because FUN=mean is the default
## (problem is silently ignored)
data$disease<- factor(data$disease, levels=rev(levels(data$disease)))
data_vaccine<-data[which(data$vaccine!=FALSE),]
## BMB: should probably use tidyverse consistently (i.e. these could be mutate/filter steps)


ggplot(data=data, aes(x=year, y=cases,colour=disease))+
  geom_line(size=2)+ geom_point(data=data_vaccine,aes(x=year,y=cases),
                          size=3,shape=20, color="black",alpha=0.9)+
  facet_wrap(.~disease, ncol = 3,scales="free")+
  theme(legend.position = 0)+ labs(title = "Line graphs about reported cases of 9 diseases by year",
       subtitle = "Black points stand for the vaccine licensed year") 
```

**BMB: explain why there are two dots in some cases? Title/subtitle are pretty good. Thanks for ordering the diseases sensibly**

Generally, for time series data, line graph is a better choice for showing changes over time.
Compared with Jia You's graph, from the Measles line graph, it is easy to understand that the number of reported cases dropped dramatically after $1964$. Moreover, for the goal to prove the importance of vaccines, more examples are more convincing. 

Although the data of different diseases are in different scales and sometimes will increase the difficulty of interpretability, we can see from those $9$ line graphs, the reported cases of majority diseases show an obvious decreasing trend after vaccines licensed. 

The drawbacks of Jia You's graph are that those circles take too much spaces for representing number of cases, the overlaps of circles make the graph become a little bit difficult to read and it is not precise enough for indicating the number of cases by the area of circles.

**BMB: all good criticisms, although the bubbles could have visual *impact* (if that's more important than precise quantitative reasoning)**

# Second GG plot
```{r warning=FALSE}

Measles_data <- data_dis[which(data_dis$disease=="Measles"),]
Measles_vaccine <- Measles_data[which(Measles_data$vaccine!=FALSE),]
dim(Measles_data)

cases_meanbyfive=c()
year_label=c()

for (i in 1:14) {
    cases_meanbyfive[i]=mean(Measles_data$cases[(5*i-4):(5*i)])
    year_label[i]<-paste(1944+(5*i-4), 1944+(5*i), sep = "-")
}    
## BMB: this can be done more efficiently (but it gets the job done);
## set up an index-by-five (e.g. seq(nrow(Measles_data)) %/% 5), then
## group_by and summarise
## try to avoid hard-coding constants in your code
## try to avoid dynamically growing arrays (see the _R Inferno_)

## BMB: be consistent about = vs <-, include spaces around these operators
Measles_data_rough=data.frame(cbind(as.numeric(cases_meanbyfive),year_label))
area_text <- rep(NA, 14)
area_text[4]="1963 \n Vaccine \n licensed"
ggplot(Measles_data_rough, aes(x=year_label, y=cases_meanbyfive))+
    geom_bar(stat = "identity")+
    theme(axis.text.x = element_text(angle=0, vjust=0.5,size=8))+
    labs(y="average number of cases",x='',
         title = "The bar chart of 5-years average reported cases of Measles from 1945 to 2014")+
    geom_text(label=area_text, colour = "blue",
                   position=position_stack(1.2), vjust=1.5) 
   
```
If our goal is to show the effectiveness of vaccines, it is not necessary for us to draw data points by year.
Here, the histogram shows the 5-years average reported cases of Measles, which sacrifices the data accuracy, but shows the effectiveness of vaccines in a simple and efficient approach, and weakens the effect of data fluctuations. 
In the first four periods, the number of cases fluctuates in a certain level, but after the period contains the event vaccine licensed, the height of the bar shrinks to nearly $\frac{1}{4}$ of previous periods.
And then though some fluctuations still happen, the number of cases shrinks in general and after the period of $1990$ to $1994$, it is nearly disappeared.


**BMB: OK. Maybe work harder on aesthetics though: scale y-axis values to thousands? Do something about x-axis labels to avoid collisions (change aspect ratio or stagger them: https://cmdlinetips.com/2020/03/ggplot2-2-3-0-is-here-two-new-features-you-must-know/ ). Do you like the default fill colour/theme?**

JD: Not sure the point of the Extra; maybe you can use it for HW3. The first picture is pretty nice, the second one is less nice. It also looks very different in the .html file compared to the one you saved. With the exponential decline in the second picture, I wonder if you thought about using a log scale. In both pictures, but especially the second, it would have been nice to make numbers more readable; here it looks like you could have reported all of your cases in thousands.


# Extra

Data set: https://www.statista.com/statistics/244615/share-of-us-persons-who-received-an-influenza-vaccination/

This data set is about the estimate influenza vaccine rates of the elder who are at least $65$ years old in U.S. from $1997$ to $2018$. The vaccine rate fluctuates by year, but in general, the vaccine rate has been improved for last $20$ years. 


**BMB: good for finding the data set.  Can you do anything with it? (e.g. compare it with influenza cases)?**

**BMB: mark 2.2/3**
